### 2021-01-29 chatbot_classification/acl_2021/abstract.tex
modified:   abstract.tex   new file:   build.sh   new file:   clear.sh   new file:   compile.sh   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   open.sh   modified:   paper.tex

\begin{abstract}
  Task-specific chatbot systems have gained many important applications, such as
  smart  speaker,  customer  service systems. One essential technique, detecting
  intention behind a user's input, can be modeled as a short text classification
  problem.  In  the early stage of buidling a chatbot, collecting enough labeled
  data  for  hundreds  of  thousands  of  user  intention  is expensive. Popular
  classfication models, direct mapping query to intention, have a high precsion,
  while depending on enough task-specific labels information. Similarity models,
  modeling  similarity  of two queries instead, can utilize out-of-domain data,
  while  having  a  relatively  lower  precision,  due  to  the  discrepency  of
  similairty loss and real classification loss. In this work, we propose a novel
  model,  called  similarity  model  fused  with  classification model (SFC), to
  combine  the  merits of the two kinds of models in the framework of multi-task
  training.  Our  extensive  experiments  on  6  public  and  1 private datasets
  demostrate  that  our  systems outperform very strong baselines (i.e., RoBERTa
  based  pretrained  model,  joint model with NER), espeically with insufficient
  data.

>>>>

\begin{abstract}
  Task-specific chatbot systems have gained many important applications, such as
  smart  speaker,  customer  service system. One fundermental module behind them, detecting
  intent of a user's input, can be modeled as a short text classification
  problem.  However, in  the early stage of buidling a chatbot, collecting enough labeled
  data  for  hundreds  of  thousands  of  user  intents is expensive. Popular
  classfication models, direct mapping a query to an intent, have a high precsion,
  while depending on enough task-specific labels information. In comparison, similarity models,
  modeling  similarity  of two queries instead, can utilize out-of-domain data,
  while  having  a  relatively  lower  precision,  due  to  the  discrepency  of
  similairty loss and real classification loss. In this work, we propose a novel
  model,  called  similarity  model  fused  with  classification model (SFC), to
  combine  the  merits of the two kinds of models in the framework of multi-task
  training.  Our  extensive  experiments  on  6  public  and  1 private datasets
  demostrate  that  our  systems outperform very strong baselines (i.e., RoBERTa
  based  pretrained  model,  joint model with NER), espeically with insufficient
  data.

### 2021-01-29 chatbot_classification/acl_2021/introduction.tex
modified:   abstract.tex   new file:   build.sh   new file:   clear.sh   new file:   compile.sh   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   open.sh   modified:   paper.tex

Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
into  many practical products. One typical example is the chatbot that shares the working burden of
human  customer  service  agents  responsible  for  customers' questions. 
Another one is intelligent  speakers, e.g. Siri, Google home. 
Regardless of whether these conversations belong to
single or  multi-round, an essential technique underlying this type of chatbot is to
identify  the  real  intention  behind  a  user's  question or reply. 
The detected intention  with  its  associated  information  is then mapped into a
predefined dialog logic graph, from which a suitable response is returned.
This  is  the  main  difference  from  a  free chatbot.

Intention detection in task-specific chatbot  is  a  challenging task due to its inherent properties. First,
a customer's  utterance  within  a conversation is usually quite short. Since it
does  not  contain  enough  information,  short  texts \cite{song2014short} are
thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
documents,  posing  a  great challenge \cite{chen2019deep} for classification
task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
initial  stage  of  building  a  chatbot , it is often rather hard to collect
sufficient  labeled  data  to  train  a good model. Developers have to
examine tons of real system logs for typical user's utterances, and then label
them  with expected intentions. Therefore, to build a task-specific chatbot with
high  performance, it is essential to solve the challenge of short-text
classification   \cite{sriram2010short}   problem   under   few-shot   setting
\cite{yu2018diverse}.

@@

The   first   one,   \emph{text  classification},  includes  classic  long  text
classification   and   short  text  classification  in  this  scenario.  Besides
traditional  machine  learning models like SVM \cite{suykens1999least}, boosting
tree  \cite{tu2005probabilistic},  many work \cite{wen2016network} choose neural
network      such      as      convolutional      neural     networks     (CNNs)
\cite{kim2014convolutional,zhang2015character,conneau2016very}  and  long  short
term  memory  networks  (LSTMs)  \cite{mousa2017contextual,liu2016recurrent}  to
accomplish  the  task  of  extracting  semantic  features from limited amount of
words.  Another two interesting lines of work, label-word
joint models, and joint NER and classification are discussed in the related work
section.  Recently,  pre-trained  language  models  on  large  corpus  like BERT
\cite{devlin2018bert}  and  RoBERTa  \cite{liu2019roberta}  has been proven more
powerful   in   solving  many  NLP  tasks  including  short-text  classification
\cite{madabushi2020cost}.       Especially      for      few-shot      scenarios
\cite{yu2018diverse},     pre-trained     models     based    on    transformers
\cite{vaswani2017attention}  tends to be more helpful to alleviate the dearth of
training data.

@@

Despite  the  success  of  these two approaches, they still have some
limitations.  
Regarding  the  \emph{text  classification  model}, when the labeled data in current
domain  is  insufficient,  it  is  quite  hard  to adopt labeled data from other
domains, as their label definitions are often incompatible to each other. Though
we can use some paraphrasing methods, e.g., machine translation based, to expand
the labeled data, the resulting benenift is still limited.
Regarding the  \emph{similarity model}, the foremost advantage is it does not pose
any restriction on label definition in a domain, as it merely models the
similarity of two input texts. Thus, we may borrow plenty of extra data to help
the similarity model training in current domain \cite{sun2019fine}. 
Yet, its biggest disadvantage is its optimization loss differs from that in a
specific task. This always lead to a suboptimial model.

>>>>

Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
into  many practical products. One typical example is the chatbot that shares the working burden of
human  customer  service  agents  responsible  for  customers' questions. 
Another one is intelligent  speakers, e.g. Siri, Google home. 
Regardless of whether these conversations belong to
single or  multi-round, an essential technique underlying this type of chatbot is to
identify  the  real  intent  behind  a  user's  question or reply. 
The detected intent  with  its  associated  information  is then mapped into a
predefined dialog logic graph, from which a suitable response is returned.
This  is  the  main  difference  from  a  free chatbot.

intent detection in task-specific chatbot  is  a  challenging task due to its inherent properties. First,
a customer's  utterance  within  a conversation is usually quite short. Since it
does  not  contain  enough  information,  short  texts \cite{song2014short} are
thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
documents,  posing  a  great challenge \cite{chen2019deep} for classification
task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
initial  stage  of  building  a  chatbot , it is often rather hard to collect
sufficient  labeled  data  to  train  a good model. Developers have to
examine tons of real system logs for typical user's utterances, and then label
them  with expected intents. Therefore, to build a task-specific chatbot with
high  performance, it is essential to solve the challenge of short-text
classification   \cite{sriram2010short}   problem   under   few-shot   setting
\cite{yu2018diverse}.

@@

The   first   one,   \emph{text  classification},  includes  classic  long  text
classification   and   short  text  classification  in  this  scenario.  Besides
traditional  machine  learning models like SVM \cite{suykens1999least}, boosting
tree  \cite{tu2005probabilistic},  many work \cite{wen2016network} choose neural
network      such      as      convolutional      neural     networks     (CNNs)
\cite{kim2014convolutional,zhang2015character,conneau2016very}  and  long  short
term  memory  networks  (LSTMs)  \cite{mousa2017contextual,liu2016recurrent}  to
accomplish  the  task  of  extracting  semantic  features from limited amount of
words.  Another two interesting lines of work, label-word
joint models, and joint NER and classification are discussed in the related work
of appendix.  Recently,  pre-trained  language  models  on  large  corpus  like BERT
\cite{devlin2018bert}  and  RoBERTa  \cite{liu2019roberta}  has been proven more
powerful   in   solving  many  NLP  tasks  including  short-text  classification
\cite{madabushi2020cost}.       Especially      for      few-shot      scenarios
\cite{yu2018diverse},     pre-trained     models     based    on    transformers
\cite{vaswani2017attention}  tends to be more helpful to alleviate the dearth of
training data.

@@

Despite  the  success  of  these two approaches, they still have some
limitations.  
Regarding  the  \emph{text  classification  model}, when the labeled data in current
domain  is  insufficient,  it  is  quite  hard  to adopt labeled data from other
domains, as their label definitions are often incompatible to each other. Though
we can use some paraphrasing methods, e.g., machine translation based, to expand
the labeled data, the resulting benefit is still limited.
Regarding the  \emph{similarity model}, the foremost advantage is it does not pose
any restriction on label definition in a domain, as it merely models the
similarity of two input texts. Thus, we may borrow plenty of extra data to help
the similarity model training in current domain \cite{sun2019fine}. 
Yet, its biggest disadvantage is its optimization loss differs from that in a
specific task. This always lead to a suboptimal model.
